---
title: "`r paste('Chlorinated Ethenes and Geochemistry Time Series Plots')`"
output:
  word_document:
    reference_docx: "blank.docx" # temp version created on download
params:
  word_graphs: NA
  wells: NA
  date_range: NA
  rendered_by_shiny: FALSE
---


```{r, include = FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)

# data from params ----------------------
word_graphs <- params$word_graphs
wells <- params$wells
date_range <- params$date_range


# dates ---------------------------
# date_format_dmy <- "%d %B %Y" # e.g 11 January 2013
date_format_mdy <- "%b %d, %Y" # e.g Jan 11 2013

# names for selected wells ---------------------
selected_wells <- set_names(wells)

# chunk options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.ext = 'AGG',
  dpi = 300
)
```


# Data filters

This report is filtered to only include:

* **`r combine_words(wells, sep = ", ")`** 
* Results from **`r format(as.Date(date_range[1]), date_format_mdy)`** to **`r format(as.Date(date_range[2]), date_format_mdy)`**

# Graph notes

* When only the year is shown on the x-axis label, this represents the start of the year
* The molar concentration graphs only plot detected data
* ORP values that are negative cannot be put in to a log10 scale graph and will not show
* If the dataset includes field duplicates, the greater of the two values is plotted.

\newpage

# Well summaries


```{r test_plots, results='asis', fig.width=8, fig.height=8}

print_if_not_null <- function(heading_text, g){
  if(!is.null(g)){
    cat(heading_text)
    print(g)
  } else {
    # nothing at all!
  }
}

print_graphs <- function(x, prog){
  cat('\n\n## `', selected_wells[x], '`\n')
  print_if_not_null('\n\n### Water Quality\n', word_graphs[[x]]$wq)
  print_if_not_null('\n\n### TOC and Redox Parameters\n', word_graphs[[x]]$tocr)
  print_if_not_null('\n\n### Chlorinated Ethene and Daughter Product Mass\n', word_graphs[[x]]$ce_norm)
  print_if_not_null('\n\n### Chlorinated Ethene and Daughter Product Mass (log10)\n', word_graphs[[x]]$ce_log10)
  print_if_not_null('\n\n### Chlorinated Ethene and Daughter Product Concentration\n', word_graphs[[x]]$ce_molar)
  
  if(params$rendered_by_shiny){
    incProgress(prog) # shiny progress
  }
}

walk(1:length(selected_wells), ~print_graphs(.x, 1/length(selected_wells)))

```





