---
# title: NA
output:
  word_document:
    reference_docx: "blank.docx" # temp version created on download
params:
  dataset: NA
  well: NA
  analyte: NA
  min_date: NA
  max_date: NA
  frac: NA
  criteria_df: NA
  molar_mass_table: NA
  conf_level: NA
  rendered_by_shiny: FALSE
---

<!-- Use this as the title instead -- it is smaller -->
# `r paste0(params$analyte, ': ',  params$well)` 


```{r, include = FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(flextable)

# # data from params ----------------------
dataset <- params$dataset
well <- params$well
analyte <- params$analyte
min_date <- params$min_date
max_date <- params$max_date
frac <- params$frac
criteria_df <- params$criteria_df
molar_mass_table <- params$molar_mass_table
conf_level <- params$conf_level
is_ggiraph <- FALSE


# dates ---------------------------
# date_format_dmy <- "%d %B %Y" # e.g 11 January 2013
date_format_mdy <- "%b %d, %Y" # e.g Jan 11 2013

# chunk options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.ext = 'AGG',
  dpi = 300
)
```

```{r}
# function for the outputs
first_order <- first_order_data(data_df = dataset, 
                                well_selected = well,
                                analyte_selected = analyte,
                                min_date = min_date,
                                max_date = max_date,
                                frac = frac,
                                criteria_df = criteria_df,
                                molar_mass_table = molar_mass_table,
                                conf_level = conf_level,
                                is_ggiraph = FALSE)
```


<!-- ## Data filters -->

This report is filtered to only include:

* Results from **`r format(as.Date(min_date), date_format_mdy)`** to **`r format(as.Date(max_date), date_format_mdy)`**
* SYS_LOC_CODE: **`r well`**
* CAS_RN: **`r dataset |> filter(CHEMICAL_NAME == analyte) |> distinct(CAS_RN) |> pull(CAS_RN)`**
* CHEMICAL_NAME: **`r analyte`**
* FRACTION: **`r frac`**

\newpage

## Dataset information

```{r}
# CDM Smith package not loaded, so we'll put this here
cdmWordTable <- function(df) {

  df %>%
    flextable(theme_fun = theme_box) %>%
    align(align = "center", part = "all" ) %>%
    font(fontname = "Calibri", part = "all") %>%
    bg(bg = "#003399", part = "header") %>%
    color(color = "white", part = "header") %>%
    border_inner_v(part = "header", border = officer::fp_border(color="white")) %>%
    fontsize(size = 8, part = "all") %>%
    height(height = ifelse(flextable_dim(.)$width<6.5, dim(.)$heights
                                      , (dim(.)$heights * ceiling(flextable_dim(.)$width/6.5)))) %>%
    width(width = dim(.)$widths*(6.5/(flextable_dim(.)$widths))) %>% 
    # edits to original table
    line_spacing(space = 0.25, part = "all")
}


```


```{r}
cdmWordTable(first_order$values_df) |> 
  height(height = 1.5, part = "header")
```

\newpage

```{r}
cdmWordTable(first_order$table)
```

\newpage

## Model coefficients

First order model

```{r}
cdmWordTable(first_order$lm_tidy)
```

Exponential first-order model

```{r}
cdmWordTable(first_order$exp_tidy)
```


## Model summary

```{r}
cdmWordTable(first_order$lm_glance)
```


## Charts

```{r}
first_order$lm_graph
```

```{r}
first_order$exp_graph
```

