---
# title: NA
output:
  word_document:
    reference_docx: "blank.docx" # temp version created on download
params:
  analyte: NA
  well: NA
  dataset: NA
  scale: NA
  slope: NA
  intercept: NA
  summary_table_wide: NA
  frac: NA
  date_range: NA
  rendered_by_shiny: FALSE
---

<!-- Use this as the title instead -- it is smaller -->
# `r paste0(params$analyte, ': ',  params$well)` 


```{r, include = FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)
library(flextable)

# data from params ----------------------
analyte <- params$analyte
well <- params$well
dataset <- params$dataset
rscale <- params$scale
slope <- params$slope
intercept <- params$intercept
summary_table_wide <- params$summary_table_wide
frac <- params$frac
date_range <- params$date_range


# dates ---------------------------
# date_format_dmy <- "%d %B %Y" # e.g 11 January 2013
date_format_mdy <- "%b %d, %Y" # e.g Jan 11 2013

# chunk options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.ext = 'AGG',
  dpi = 300
)
```

```{r}
# this works because there is only one location/ well group due to the filters
lgc <- unique(dataset$LOC_GROUP_CODE)
mag <- unique(dataset$METHOD_ANALYTE_GROUP)
slc <- unique(dataset$SYS_LOC_CODE)
casrn <- unique(dataset$CAS_RN)
cn <- unique(dataset$CHEMICAL_NAME)
un <- unique(dataset$REPORT_RESULT_UNIT)
```


<!-- ## Data filters -->

This report is filtered to only include:

* Results from **`r format(as.Date(date_range[1]), date_format_mdy)`** to **`r format(as.Date(date_range[2]), date_format_mdy)`**
* SYS_LOC_CODE: **`r slc`**
* CAS_RN: **`r casrn`**
* CHEMICAL_NAME: **`r cn`**
* REPORT_RESULT_UNIT: **`r un`**
* FRACTION: **`r frac`**

## Time series graph

* When only the year is shown in the x-axis label, this represents the start of the year
* ORP values that are negative cannot be put in to a log10 scale graph and will not show.

```{r, results='asis', fig.width=8, fig.height=6}
# the graph -- initial then conditional depending on scale
p1 <- single_dataset_graph_initial_ggg(dataset, rscale)

if(rscale == "log"){
  p1 +
    geom_smooth(data = dataset %>%
                  filter(DETECT_FLAG == "Y"),
                colour = "blue",
                se = FALSE,
                size = 0.5)
} else {
  p1 +
    geom_abline(aes(slope = slope,
                    intercept = intercept,
                    colour = "Theil-Sen Line"),
                colour = "blue")
}

```

\newpage

## Boxplot

```{r, results='asis', fig.width=8, fig.height=4}
single_dataset_jittered_boxplot(dataset)
```

\newpage

## Dataset values


```{r}
# CDM Smith package not loaded, so we'll put this here
cdmWordTable <- function(df) {

  df %>%
    flextable(theme_fun = theme_box) %>%
    align(align = "center", part = "all" ) %>%
    font(fontname = "Calibri", part = "all") %>%
    bg(bg = "#003399", part = "header") %>%
    color(color = "white", part = "header") %>%
    border_inner_v(part = "header", border = officer::fp_border(color="white")) %>%
    fontsize(size = 8, part = "all") %>%
    height(height = ifelse(flextable_dim(.)$width<6.5, dim(.)$heights
                                      , (dim(.)$heights * ceiling(flextable_dim(.)$width/6.5)))) %>%
    width(width = dim(.)$widths*(6.5/(flextable_dim(.)$widths))) %>% 
    # edits to original table
    line_spacing(space = 0.25, part = "all")
}

cdmWordTable(dataset %>% 
               select(SAMPLE_DATE, REPORT_RESULT_VALUE, INTERPRETED_QUALIFIERS))
```

\newpage

## Statistics

```{r}
summary_table_wide %>% 
  select(-(SYS_LOC_CODE:`Dataset end`)) %>% 
  mutate(across(everything(), as.character)) %>% 
  pivot_longer(cols = everything()) %>% 
  rename(Item = name,
         Value = value) %>% 
  cdmWordTable()
```

<!-- ## Dataset details -->

<!-- # ```{r} -->
<!-- # cdmWordTable(summary_table_wide[1:11]) -->
<!-- # ``` -->

<!-- ## Parameter estimate details -->

<!-- ```{r} -->
<!-- cdmWordTable(summary_table_wide[12:16]) -->
<!-- ``` -->

<!-- ## Confidence limit details -->

<!-- ```{r} -->
<!-- cdmWordTable(summary_table_wide[17:23]) -->
<!-- ``` -->

<!-- ## Trend details -->

<!-- ```{r} -->
<!-- cdmWordTable(summary_table_wide[24:31]) -->
<!-- ``` -->

