---
title: "Sum of Total Volatile Organic Compounds"
subtitle: "`r params$subtitle`"
output:
  word_document:
    reference_docx: "blank.docx" # temp version created on download
params:
  word_mass_graph: NA
  word_molar_graph: NA
  subtitle: NA
  wells: NA
  chems: NA
  date_range: NA
  rendered_by_shiny: NA
---


```{r, include = FALSE}
library(tidyverse)
library(lubridate)
library(scales)
library(knitr)

# data from params ----------------------
word_mass_graph <- params$word_mass_graph
word_molar_graph <- params$word_molar_graph
wells <- params$wells
chems <- params$chems
date_range <- params$date_range

# dates ---------------------------
# date_format_dmy <- "%d %B %Y" # e.g 11 January 2013
date_format_mdy <- "%b %d, %Y" # e.g Jan 11 2013

# chunk options
knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE,
  echo = FALSE,
  fig.ext = 'AGG',
  dpi = 300
)

```


# Data filters
This report is filtered to only include:

* These wells: **`r combine_words(wells, sep = ", ")`**
* Chemicals summed to calculate total VOC concentrations: **`r combine_words(chems, sep = ", ")`**
* Results from **`r format(as.Date(date_range[1]), date_format_mdy)`** to **`r format(as.Date(date_range[2]), date_format_mdy)`**

# Graph notes

* When only the year is shown in the x-axis label, this represents the start of the year.

\newpage


```{r test_plots, results='asis', fig.width=8, fig.height=6}
print(word_mass_graph)
print(word_molar_graph)
```
